---
title: "Advanced R (2nd ed)"
output: 
  html_notebook:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

# IV Metaprogramming - Chapter 17

## 17.1 Introduction

```{r}
library(rlang)
library(lobstr)
```

## 17.2 Code is data

```{r}
expr(mean(x, na.rm = TRUE))

expr(10 + 100 + 1000)
```

```{r}
capture_it <- function(x) {
  expr(x)
}

capture_it(a + b + c)
```

```{r}
capture_it <- function(x) {
  enexpr(x)
}

capture_it(a + b + c)
```

Complex expressions behave much like lists. That means you can modify them using `[[` and `$`.

```{r}
f <- expr(f(x = 1, y = 2))
f
f$x
f$y

f$z <- 3
f
f$z

f[[1]]
f[[2]]
f[[3]]
f[[4]]

f[[2]] <- NULL
f
```

## 17.3 Code is a tree

Almost every programming language represents code as a tree, often called the abstract syntax tree, or AST for short. R is unusual in that you can actually inspect and manipulate this tree.

Function calls form the branches of the tree, and are shown by rectangles. The leaves of the tree are symbols (like a) and constants (like "b").

```{r}
lobstr::ast(f(a, "b"))
```

Nested function calls create more deeply branching trees.

```{r}
lobstr::ast(f1(f2(a, b), f3(1, f4(2))))
```

Because all function forms in R can be written in prefix form (Section 6.8.2), every R expression can be displayed in this way.

```{r}
lobstr::ast(1 + 2 * 3)

lobstr::ast(1 * 2 + 3)

lobstr::ast(1 * 2 + 3 * 4)
```

## 17.4 Code can generate code

```{r}
call2("f", 1, 2, 3)

call2("+", 1, call2("*", 2, 3))

call2("+", call2("*", 1, 2), 3)

call2("+", call2("*", 1, 2), call2("*", 3, 4))

x <- 3
call2("+", 1, x)
rm(x)
```

`call2()` is often convenient to program with, but is a bit clunky for interactive use. An alternative technique is to build complex code trees by combining simpler code trees with a template. `expr()` and `enexpr()` have built-in support for this idea via `!!` (pronounced bang-bang), the **unquote operator**.

Basically `!!x` inserts the code tree stored in `x` into the expression. This makes it easy to build complex trees from simple fragments.

```{r}
xx <- expr(x + x)
yy <- expr(y + y)

expr(!!xx / !!yy)
```

```{r}
cv <- function(var) {
  var <- enexpr(var)
  expr(sd(!!var) / mean(!!var))
}

cv(x)

cv(x + y)
```

```{r}
cv(`)`)
```

## 17.5 Evaluation runs code

The primary tool for evaluating expressions is `base::eval()`, which takes an expression and an environment.

```{r}
eval(expr(x + y), env(x = 1, y = 2))
```

```{r}
eval(expr(x + y), env(x = 100, y = 2))
```

```{r}
# sd(1:5) / mean(1:5)
eval(cv(x), env(x = 1:5))
```

If you omit the environment, eval uses the current environment.

```{r}
x <- 10
y <- 100
eval(expr(x + y))
```

One of the big advantages of evaluating code manually is that you can tweak the environment. There are two main reasons to do this:

1. To temporarily override functions to implement a domain specific language.
2. To add a data mask so you can to refer to variables in a data frame as if they are variables in an environment.

## 17.6 Customizing evaluation with functions

The above example used an environment that bound x and y to vectors. It’s less obvious that you also bind names to functions, allowing you to override the behaviour of existing functions.

Here code is evaluated in a special environment where `*` and `+` have been overridden to work with strings instead of numbers.

```{r}
string_math <- function(x) {
  e <- env(
    caller_env(),
    `+` = function(x, y) paste0(x, y),
    `*` = function(x, y) strrep(x, y)
  )
  
  eval(enexpr(x), envir = e)
}

name <- "Hadley"
string_math("Hello " + name)

string_math(("x" * 2 + "-y ") * 3)
```

## 17.7 Customizing evaluation with data

Rebinding functions is an extremely powerful technique, but it tends to require a lot of investment. A more immediately practical application is modifying evaluation to look for variables in a data frame instead of an environment.

It’s possible to use `eval()` for this, but there are a few potential pitfalls, so we’ll switch to `rlang::eval_tidy()` instead.

```{r}
df <- data.frame(x = 1:5, y = sample(5))
# df

eval_tidy(expr = expr(x + y), data = df)
```

Evaluating with a data mask is a useful technique for interactive analysis because it allows you to write `x + y` rather than `df$x + df$y`. However, that convenience comes at a cost: ambiguity. In Section 20.4 you’ll learn how to deal ambiguity using special `.data` and `.env` pronouns.

We can wrap this pattern up into a function by using `enexpr()`. This gives us a function very similar to `base::with()`.

```{r}
with2 <- function(df, expr) {
  eval_tidy(enexpr(expr), df)
}

with2(df, x + y)
```

Unfortunately this function (`with2()`) has a subtle bug and we need a new data structure to deal with it.

## 17.8

Notice what happens when we put an `a` variable inside the `with2()` function.

```{r}
with2 <- function(df, expr) {
  a <- 1000
  eval_tidy(enexpr(expr), df)
}
```

We want the value of `a` to come from the binding we can see (10), not the binding internal to the function (1000).

```{r}
df <- data.frame(x = 1:3)
a <- 10
with2(df, x + a)
```

We can solve this problem by using a new data structure: a quosure. The quosure bundles an expression with an environment. `eval_tidy()` knows how to work with quosures, so we only need to use `enquo()` instead of `enexpr()`.

```{r}
with2 <- function(df, expr) {
  a <- 1000
  eval_tidy(enquo(expr), df)
}

with2(df, x + a)
```

Whenever you use a data mask, you have to always use `enquo()` instead of `enexpr()`.



```{r echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
