---
title: "Advanced R (2nd ed)"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

# IV Metaprogramming - Chapter 18 - Expressions

## 18.1 Introduction

```{r}
y <- x * 10
```

The above doesn't work because we haven't define a variable called `x`.

It'd be nice if we could capture the intent of the code without executing it.

```{r}
z <- rlang::expr(y <- x * 10)
z
```

`expr()` returns an expression, an object that captures the structure of the code without evaluating it. If you have an expression, you can run it with `base::eval()`.

```{r}
x <- 4
eval(z)
```


```{r}
library(rlang)
library(lobstr)
```

## 18.2 Abstract syntax trees

### 18.2.1 Drawing

```{r}
lobstr::ast(f(x, "y", 1))
```

```{r}
lobstr::ast(f(g(1, 2), h(3, 4, i())))
```

### 18.2.2 Non-code components

The "abstract" in "abstract syntax tree" is because whitespace is (mostly) meaningless.

```{r}
lobstr::ast(
  f  ( x   ,       y   ) # important
)
```

Here's an example where whitespace matters.

```{r}
lobstr::ast(y <- x)
lobstr::ast(y < -x)
```

### 18.2.3 Infix calls

Every call in R can be written in tree form because any call in R can be written in prefix form.

`y <- x * 10` can be written in prefix form as `` `<-`(y, `*`(x, 10)) ``.

```{r}
lobstr::ast(y <- x * 10)
```

if you generate an expression with prefix calls, R will still print it in infix form.

```{r}
expr(`<-`(y, `*`(x, 10))) # prefix operator form
expr(y <- x * 10)         # infix operator form
```

### 18.2.4 Exercises

1. Reconstruct the code represented by the trees below:

```
#> █─f 
#> └─█─g 
#>   └─█─h
```

```{r}
lobstr::ast(f(g(h())))
```

```
#> █─`+` 
#> ├─█─`+` 
#> │ ├─1 
#> │ └─2 
#> └─3
```

```{r}
lobstr::ast(1 + 2 + 3)
```

```
#> █─`*` 
#> ├─█─`(` 
#> │ └─█─`+` 
#> │   ├─x 
#> │   └─y 
#> └─z
```

```{r}
lobstr::ast((x + y) * z)
```

2. Draw the following trees by hand then check your answers with `lobstr::ast()`.

`f(g(h(i(1, 2, 3))))`

```{r}
lobstr::ast(f(g(h(i(1, 2, 3)))))
```

`f(1, g(2, h(3, i())))`

```{r}
lobstr::ast(f(1, g(2, h(3, i()))))
```

`f(g(1, 2), h(3, i(4, 5)))`

```{r}
lobstr::ast(f(g(1, 2), h(3, i(4, 5))))
```

3. What’s happening with the ASTs below? (Hint: carefully read `?"^"`)

(a)
```{r}
lobstr::ast(`x` + `y`)
lobstr::ast(x + y)
lobstr::ast(`x`)
lobstr::ast(x)
```

This seems straightforward. `x` and ```x``` both express the same symbol: `x`.

(b)
```{r}
lobstr::ast(x ** y)
```

Here, the following expressions are all the same:

* `x ^ y`
* ```^`(x, y)``
* `x ** y`

```{r}
lobstr::ast(x ^ y)
lobstr::ast(`^`(x, y))
lobstr::ast(x ^ y)
```

As the documentation in `?"^"` says, "`**` is translated in the parser to `^`, but this was undocument for many years... Even though it (i.e., the infix binary operator `**`) had been deprecated in S for 20 years, it was still accepted in R in 2008."

(c)
```{r}
lobstr::ast(1 -> x)
```

The `<-` assignment operator in R actually works in both directions: `<-` or `->`. `x <- 1` assigns the value of 1 to the variable `x`, and `1 -> x` does the same thing. They both can be expressed as `` `<-`(x, 1)``.

The following are all the same: 

* `x <- 1`
* `1 -> x`
* ```<-`(x, 1)``

```{r}
lobstr::ast(x <- 1)
lobstr::ast(1 -> x)
lobstr::ast(`<-`(x, 1))
```



```{r echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
