---
title: "Tidy Evaluation - Part I Principles - Chapter 2"
author: "Nicolas May"
date: "2/2/2019"
output: 
  html_document:
    theme: cerulean
    highlight: espresso
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

# 4 Getting up to speed

## 4.1 Writing functions

### 4.1.1 Reducing duplication

```{r}
library(dplyr)
```


```{r}
df <- tibble(
  a = sample(1:100, size = 10),
  b = sample(1:1000, size = 10),
  c = sample(-100:1, size = 10),
  d = c(sample(1:10000, size = 5), NA_integer_, sample(1:10000, size = 4))
)
```

```{r}
(df$a - min(df$a)) / (max(df$a) - min(df$a))
(df$b - min(df$b)) / (max(df$b) - min(df$b))
(df$c - min(df$c)) / (max(df$c) - min(df$c))
(df$d - min(df$d)) / (max(df$d) - min(df$c))
```

```{r}
rescale01 <- function(num) {
  (num - min(num)) / (max(num) - min(num))
}
```

```{r}
rescale01(df$a)
rescale01(df$b)
rescale01(df$c)
rescale01(df$d)
```

```{r}
rescale01 <- function(num) {
  rng <- range(num, na.rm = TRUE, finite = TRUE)
  (num - rng[[1]]) / (rng[[2]] - rng[[1]])
}
```

```{r}
rescale01(df$a)
rescale01(df$b)
rescale01(df$c)
rescale01(df$d)
```

```{r}
df1 <- 
  ```

```{r}
# df1 %>% group_by(x1) %>% summarise(mean = mean(y1))
# df2 %>% group_by(x2) %>% summarise(mean = mean(y2))
# df3 %>% group_by(x3) %>% summarise(mean = mean(y3))
# df4 %>% group_by(x4) %>% summarise(mean = mean(y4))
```

```{r}
# data %>% group_by(group_var) %>% summarise(mean = mean(summary_var))
```

```{r}
# this doesn't work
grouped_mean <- function(data, group_var, summary_var) {
  data %>%
    group_by(group_var) %>%
    summarise(mean = mean(summary_var))
}
```

```{r}
grouped_mean(mtcars, cyl, mpg)
```

```{r}
# this works
grouped_mean <- function(data, group_var, summary_var) {
  group_var <- enquo(group_var)
  summary_var <- enquo(summary_var)
  
  data %>% 
    group_by(!!group_var) %>% 
    summarize(mean = mean(!!summary_var))
}
```

```{r}
grouped_mean(mtcars, cyl, mpg)
```

### 4.1.2 What's special about quoting functions?

Two kinds of functions in R... evaluating functions and quoting functions.

Evaluating functions take arguments as _**values**_. R computes the argument values following the standard rules of evaluation. So evaulating functions are passed the value of the expression.

The simplest evaluating function is `identity`. It evaluates its single argument and returns the value.

```{r}
identity(6)

identity(2 * 3)

a <- 2
b <- 3
identity(a * b)
```

Quoting functions are _not_ passed the value of the expression; instead, quoting functions are passed the _**expressions themselves**_.

We say the argument has been automatically quoted.

The simplest quoting function is `quote`. It automatically quotes its argument and returns the quoted expression without any evaluation. 

```{r}
quote(6)

quote(2 * 3)

a <- 2
b <- 3
quote(a * b)
```

Other familiar quoting operators are `"` and `~`.

```{r}
"a * b" # returns a * b as a string... it doesn't evaluate a * b == 2 * 3

~ a * b

quote(a * b)
```

#### 4.1.2.1 Quoting and evaluating in mundane R code

```{r}
df <- data.frame(
  y = 1,
  var = 2
)
```

```{r}
df
```

```{r}
df$y

var <- "y"
df[[var]]
```

`[[` is an evaluating function while `$` is a quoting function.

You can indirectly refer to columns with `[[` because the subsetting index is evaluated.

```{r}
df[[var]] # indirect

df[["y"]] # direct
```

But quoted expressions can only be direct.

```{r}
df$y   # direct

df$var # direct
```

#### 4.1.2.2 Detecting quoting functions

```{r}
library(MASS)

mtcars2 <- subset(mtcars, cyl == 4)

sum(mtcars2$am)

rm(mtcars2)
```

A good indication that an argument is autoquoted and evaluated in a special was is that the argument won't work correctly outside its original context.

1. `library(MASS)`

```{r}

temp <- MASS

temp <- "MASS"

library(temp)
```

Doesn't work because there is no `MASS` object to find and `library` interprets `temp` directly as a package name.

2. `mtcars2 <- subset(mtcars, cyl == 4)`
```{r}
temp <- cyl == 4
```

Doesn't work because R can't find `cyl`... we haven't specified where to find `cyl`.

3. `sum(mtcars2$am)`
```{r}
temp <- mtcars$am

sum(temp)
```

Works because `sum` is an evaluating function.

4. `rm(mtcars2)`
```{r}
mtcars2 <- mtcars
temp <- "mtcars2"
rm(temp)

exists("mtcars2")
exists("temp")
```

`rm` autoquotes its arguments, so it removed the object referred to as `temp` (which is the string "mtcars"). 

### 4.1.3 Unquotation

Functions that evaluate their arguments are easier to program with because they support both direct and indirect references. For quoting functions, a piece of syntax is missing. We need the ability to unquote arguments.

#### 4.1.3.1 Unquoting in base R

There is no general unquoting convention in base R so you have to read the documentation to figure out how to unquote an argument. Many functions like `subset()` or `transform()` do not provide any unquoting option at all.

#### 4.1.3.2 Unquoting in the tidyverse!!

All quoting functions in the tidyverse support a single unquotation mechanism, the `!!` operator. 

Unquoting lets you open a variable and use what’s inside instead.

```{r}
glimpse(mtcars)
```

```{r}
# variables referring to columns `cyl` and `mpg`
x_var <- quote(cyl)
y_var <- quote(mpg)
```

```{r}
x_var
y_var
```

In `dplyr` most verbs quote their arguments.

```{r}
library("dplyr")

by_cyl <- mtcars %>% 
  group_by(!!x_var) %>%            # unquote / open x_var
  summarize(mean = mean(!!y_var))  # unquote / open y_var
```

```{r}
by_cyl
```

In `ggplot2` `aes()` is the main quoting function.

```{r}
library("ggplot2")
```

```{r}
ggplot(mtcars, aes(!!x_var, !!y_var)) +  # Open x_var and y_var
  geom_point()
```

`ggplot2` also features `vars()` which is useful for facetting.

```{r}
ggplot(mtcars, aes(disp, drat)) +
  geom_point() +
  facet_grid(vars(!!x_var))  # Open x_var
```

### 4.1.4 Understanding `!!` with `qq_show()`

```{r}
rlang::qq_show(
  mtcars %>% group_by(!!x_var)
)
```

```{r}
rlang::qq_show(
  data %>% 
    summarise(mean = mean(!!y_var))
)
```

```{r}
rlang::qq_show(
  data %>% 
    group_by(!!x_var) %>% 
    summarize(mean = mean(!!y_var))
)
```


```{r}
rlang::qq_show(
  ggplot(mtcars, aes(!!x_var, !!y_var)) +
    geom_point()
)
```

```{r}
rlang::qq_show(
  ggplot(mtcars, aes(disp, drat)) +
    geom_point() +
    facet_grid(vars(!!x_var))
)
```

## 4.2 Quote and unquote

The basic process for creating tidyeval functions requires thinking a bit differently but is straightforward: quote and unquote.

1. Use enquo() to make a function automatically quote its argument.
2. Use !! to unquote the argument.

### 4.2.1 The abstraction step

We start as usual by identifying the varying parts of a computation and giving them informative names. These names become the arguments to the function.

```{r}
grouped_mean <- function(data, group_var, summary_var) {
  data %>% 
    group_by(group_var) %>% 
    summarize(mean = mean(summary_var))
}
```

This of course doesn't quite work. So we'll fix it.

### 4.2.2 The quoting step

We know that the fundamental quoting function is `quote()` but how do we go about creating other quoting functions? This is the job of `enquo()`. While `quote()` quotes what you typed, `enquo()` quotes what your user typed. In other words it makes an argument automatically quote its input. This is exactly how dplyr verbs are created!

```{r}
grouped_mean <- function(data, group_var, summary_var) {
  group_var <- enquo(group_var)      ## <== HERE
  summary_var <- enquo(summary_var)  ## <== HERE
  
  data %>% 
    group_by(group_var) %>% 
    summarize(mean = mean(summary_var))
}
```

### 4.2.3 The unquoting step

Finally we identify any place where these variables are passed to other quoting functions. That’s where we need to unquote with `!!`.

```{r}
grouped_mean <- function(data, group_var, summary_var) {
  group_var <- enquo(group_var)
  summary_var <- enquo(summary_var)
  
  data %>% 
    group_by(!!group_var) %>%              ## <== HERE
    summarize(mean = mean(!!summary_var))  ## <== HERE
}
```

### 4.2.4 Result

```{r}
grouped_mean <- function(data, group_var, summary_var) {
  group_var <- enquo(group_var)
  summary_var <- enquo(summary_var)
  
  data %>% 
    group_by(!!group_var) %>%
    summarize(mean = mean(!!summary_var))
}
```

```{r}
grouped_mean(mtcars, cyl, mpg)
```

```{r}
grouped_mean(mtcars, cyl, disp)
```

```{r}
grouped_mean(mtcars, am, disp)
```

## 4.3 Strings instead of quotes

















